Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-29 cbm-rbd-paper.tex
simulation figures ready

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}
\newcommand{\tthresh}{\tau_{\text{thresh}}}
\newcommand{\tstarnow}{t_*^{(\tnow)}}
\newcommand{\gstarnow}{g_*^{(\tnow)}}
\newcommand{\gtotalnow}{g_\text{total}^{(\tnow)}}

@@

During a cycle,
$\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
This is feasible because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
and determine $\tausnow$ with a simple grid search.
Updating $\tausnow$ frequently is useful because,
even in absence of failures of system components,
all components age, and also non-failure adds information to the component models.
Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
as is visible in the top left panel of Figure~\ref{fig:tauhist1fig2}.
%An alternative would be to update $\tausnow$ only when a component fails,
%but as a (near) real-time update of $\tausnow$ is possible and useful,
%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim1fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated according to prior parameters.}
\label{fig:br1sim1fig5Tt01}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
\label{fig:br1sim2fig5Tt01}
\end{figure}

@@

\begin{figure}
%\includegraphics[width=\textwidth]{br1sim3fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
\label{fig:br1sim3fig5Tt01}
\end{figure}

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}
\newcommand{\tthresh}{\tau_{\text{thresh}}}
\newcommand{\tstarnow}{t_*^{(\tnow)}}
\newcommand{\gstarnow}{g_*^{(\tnow)}}
\newcommand{\gtotalnow}{g_\text{total}^{(\tnow)}}
\newcommand{\esys}{e_\text{sys}}
\newcommand{\mrsys}{\bar{r}_\text{sys}}

@@

During a cycle,
$\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
This is feasible because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
and determine $\tausnow$ with a simple grid search.
Updating $\tausnow$ frequently is useful because,
even in absence of failures of system components,
all components age, and also non-failure adds information to the component models.
Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T}.
%An alternative would be to update $\tausnow$ only when a component fails,
%but as a (near) real-time update of $\tausnow$ is possible and useful,
%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.

@@

$\esys$ is the number of system failures,
$\mrsys$ is the mean realized system runtime (I called this 'cycle length' before),
$\bar{g}$ is the mean realized unit cost rate.

CBM = condition-based maintenance
ABM = age-based maintenance
CM = corrective maintenance
cpu = continuous parameter update
epu = end of cycle parameter update
npu = no parameter update

@@

Obviously, CM has always 5 system failures in the 5 cycles, while CBM and ABM (mostly) avoid system failures. Mean system runtimes are longest for CM because it runs the system until failure, but this leads to the highest mean unit cost rates. CBM with continuous parameter update has the lowest mean unit cost rate since it has the longest system runtimes without failures. The age-based policy without parameter update always schedules maintenance for $\tau_*^{(0)} = 1.6$, and as the system does not fail before this time in any of the simulations, the system runtime is always 1.6 and the unit cost rate is $0.2 / 1.6 = 0.125$.

\begin{figure}
\includegraphics[width=\textwidth]{br1sim1fig5Tt01ac}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated according to prior parameters.}
\label{fig:br1sim1fig5Tt01}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5Tt01ac}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
\label{fig:br1sim2fig5Tt01}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim3fig5Tt01ac}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
\label{fig:br1sim3fig5Tt01}
\end{figure}
